ms2

### 2017-06-20 ms2/ms2.Rmd
updating filtering

raw_abg = read_tsv('../../../antibiogram/data/abg.tsv', col_types=cols(zipcode='c')) %>%
  mutate(drug=tolower(drug), percent_nonsusceptible=100-percent_susceptible) %>%
  left_join(hrr, by=c('zipcode', 'state')) %>%
  right_join(resistance_groups, by='drug') %>%
  select(bug, drug, drug_group, state, hrr, percent_nonsusceptible, n_isolates)

# Keep only the abundant bug/drug combinations
min_n_states = 35
good_combos = semi_join(raw_abg, possible_bug_drug, by=c('bug', 'drug_group')) %>%
  select(bug, drug_group, state) %>%
  distinct %>%
  count(bug, drug_group) %>% ungroup() %>% 
  rename(n_places=n) %>%
  filter(n_places >= min_n_states)

abg = raw_abg %>%
  #mutate(raw_bug=bug) %>%
  # shorten the bug names
  left_join(bug_names, by='bug') %>%
  select(-bug) %>% rename(bug=bug_short) %>%
  # group the different S. aureus into meta-groups depending on the drug
  left_join(bug_groups, by=c('bug', 'drug_group')) %>%
  mutate(bug_group=if_else(is.na(bug_group), bug, bug_group)) %>%
  select(-bug) %>% rename(bug=bug_group) %>%
  right_join(good_combos, by=c('bug', 'drug_group')) %>%
  # keep only particular bug/drug combos
  right_join(possible_bug_drug, by=c('bug', 'drug_group')) #%>%
  #filter(!is.na(percent_nonsusceptible), !is.na(n_isolates))

@@

# replace the NA number of isolates with the median for that bug/drug
abg %<>%
  left_join(median_n_isolates) %>%
  mutate(n_isolates=if_else(is.na(n_isolates), median_n_isolates, n_isolates)) %>%
  select(-median_n_isolates)

>>>>

raw_abg = read_tsv('../../../antibiogram/data/abg.tsv', col_types=cols(zipcode='c')) %>%
  mutate(drug=tolower(drug), percent_nonsusceptible=100-percent_susceptible) %>%
  left_join(hrr, by=c('zipcode', 'state')) %>%
  right_join(resistance_groups, by='drug') %>%
  select(bug, raw_drug=drug, drug_group, state, hrr, percent_nonsusceptible, n_isolates)

# Keep only the abundant bug/drug combinations
# min_n_states = 35
# good_combos = semi_join(raw_abg, possible_bug_drug, by=c('bug', 'drug_group')) %>%
#   select(bug, drug_group, state) %>%
#   distinct %>%
#   count(bug, drug_group) %>% ungroup() %>% 
#   rename(n_places=n) %>%
#   filter(n_places >= min_n_states)

abg = raw_abg %>%
  #mutate(raw_bug=bug) %>%
  # shorten the bug names
  left_join(bug_names, by='bug') %>%
  select(-bug) %>% rename(bug=bug_short) %>%
  # group the different S. aureus into meta-groups depending on the drug
  left_join(bug_groups, by=c('bug', 'drug_group')) %>%
  mutate(bug_group=if_else(is.na(bug_group), bug, bug_group)) %>%
  select(-bug) %>% rename(bug=bug_group) %>%
  #right_join(good_combos, by=c('bug', 'drug_group')) %>%
  # keep only particular bug/drug combos
  right_join(possible_bug_drug, by=c('bug', 'drug_group'))
  #filter(!is.na(percent_nonsusceptible), !is.na(n_isolates))

@@

# get the number of states in which each bug/drug appears
min_n_states = 37
abg_n_states = abg %>%
  select(bug, drug_group, state) %>%
  distinct() %>%
  count(bug, drug_group) %>%
  ungroup() %>%
  rename(n_states=n)
abg_n_hrr = abg %>%
  select(bug, drug_group, hrr) %>%
  distinct() %>%
  count(bug, drug_group) %>%
  ungroup() %>%
  rename(n_hrr=n)

# replace the NA number of isolates with the median for that bug/drug
abg %<>%
  left_join(median_n_isolates) %>%
  mutate(n_isolates=if_else(is.na(n_isolates), median_n_isolates, n_isolates)) %>%
  select(-median_n_isolates) %>%
  left_join(abg_n_states, by=c('bug', 'drug_group')) %>%
  left_join(abg_n_hrr, by=c('bug', 'drug_group'))
  #filter(n_places >= min_n_states)
